---
title: "Making MouseBuettnerTCell package"
author: "Joyce Hsiao"
date: "2016-12-08"
output:
  html_document:
    css: floating-toc.css
    toc: true
---


```{r, include = FALSE}
library(knitr)
opts_chunk$set(eval = FALSE, echo = TRUE)
```


### Load packages

```{r}
library(data.table)
library(Biobase)
library(xlsx)
```


### Data description from Buettner et al. 2015

Buettner et al., 2015, differentation TCells

>>> [...] Duplets and cells with low yield or poor quality cDNA were removed, yielding 81 cells for analysis. After normalization and estimation of technical noise using ERCC spike-ins (see RNA-seq normalization and estimation of technical noise), we retained a set of 7,073 genes for analysis with variation above the technical background level (FDR <0.1; Supplementary Data 2).

>>> [...] Raw read counts were normalized using the approach proposed in DESeq47, deriving size factors for each cell from the ERCC spike-ins. Estimates of the technical variability were also derived using the ERCC spike-ins, adapting the approach in Brennecke et al.20 (Supplementary Fig. 1a).


### Load data

```{r, eval = FALSE}
# import count matrix, convert to a matrix object
T_cells <- read.csv('../data/HumanBuettnerTCell/nbt.3102-S7-sheet1.csv', 
                     header = TRUE, fill = TRUE,
                     stringsAsFactors = FALSE)
T_cells <- T_cells[,-1]
T_cells <- t(T_cells)
T_cells <- T_cells[1:7073, ]

# make a count matrix
counts <- T_cells
colnames(counts) <- rep(1:NCOL(counts))

# feature info
gene_info <- data.frame(gene_names = rownames(counts))
row_data <- gene_info
rownames(row_data) <- gene_info$gene_names
```

Phenotype info

```{r make-pheno}
# import cluster assignment determined in the original paper Buettner et al., 2015

cluster_list <- read.csv('../data/HumanBuettnerTCell/nbt.3102-S7-sheet3.csv', 
                     header = TRUE, fill = TRUE,
                     stringsAsFactors = FALSE)

meta_list <- data.frame(labelDescription = c("cellID", "Cluster (Gata3 High)"),
                    row.names = c("cellID", "Cluster"))
col_data <- data.frame(cellID = as.character(seq(1:NCOL(counts))),
                       Cluster = cluster_list[ ,2])

rownames(col_data) <- colnames(counts)
stopifnot(all.equal(rownames(col_data), colnames(counts)))
```

Putting all together

```{r make eset}
HumanBuettnerTCell <- new("ExpressionSet",
                exprs = as.matrix(counts),
                phenoData = new("AnnotatedDataFrame",
                                data = col_data,
                                varMetadata = meta_list),
                featureData = new("AnnotatedDataFrame",
                                  data = row_data),
                experimentData = new("MIAME",
                                     title = "Buttner Human T cells"))


save(HumanBuettnerTCell,
        file = "../data/all-rda/HumanBuettnerTCell.rda")
```



### Session information

```{r, echo = FALSE}
sessionInfo()
```

